---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


This is a message from Grace
Test Anna
Katie test


```{r setup, include=FALSE}

library(classdata)
data(ames)
head(ames)
?ames

```





The variables for the Ames data are:
Parcel ID: ID of the character (Integer) 
```{r setup, include=FALSE}
range(ames$'Parcel ID', na.rm = TRUE)
```


Address: Property address in Ames, IA (String)
We cannot find a range of this variable
Style: Type and build of housing (String)
We cannot find a range of this variable
Occupancy: Type of family ownership and owner details (String)

We cannot find a range for this variable



Sale Date: Date of Sale written as Year_Month_Day
-We expect the Range to be similar to the Year Built
Sale Price: Sale Price in US Dollars (Integers)
```{r setup, include=FALSE}
range(ames$'Sale Price', na.rm = TRUE)

```
Multi Sale: If the sale was part of a package (Logical Value)
-The range is not very important for here becuase there is only two values (yes and no for part of a package)
Year Built: Year that house was built (Integer Value)
```{r setup, include=FALSE}
range(ames$YearBuilt, na.rm = TRUE)

```

Acres: Float
TotalLiving Area: int
Bedrooms:int
Finished basement: int

Lot Area:
AC:
Fire Place:
Neightborhood:


2. Our main variable is sale price


