---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

<<<<<<< HEAD

=======
>>>>>>> 1653ac9857c4f8c8784148645096f49a73517cf8
This is a message from Grace
Test Anna
Katie test


```{r setup, include=FALSE}

library(classdata)
data(ames)
head(ames)
?ames

```





The variables for the Ames data are:
Parcel ID: ID of the character (Integer) 
Address: Property address in Ames, IA (String)
Style: Type and build of housing (String)
Occupancy: Type of family ownership and owner details (String)
<<<<<<< HEAD
Sale Date: 
Sale Price: 
Multi Sale:
Year Built:
Acres: Acres of the lot. (Float)
TotalLiving Area: Total living area in square feet (Integer)
Bedrooms: Number of bedrooms (Integer)
Finished basement: Total area of the finshed basement in square feet (Integer)
=======
Sale Date: Date of Sale written as Year_Month_Day
Sale Price: Sale Price in US Dollars (Integers)
Multi Sale: If the sale was part of a package (Logical Value)
Year Built: Year that house was built (Integer Value)
Acres: Float
TotalLiving Area: int
Bedrooms:int
Finished basement: int
>>>>>>> 933549a44bec7215ce6bafe13eeb4a0c88c38a52
Lot Area:
AC:
Fire Place:
Neightborhood:


2. Our main variable is sale price


