---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab report #2

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


This is a message from Grace
Test Anna
Katie test


```{r setup, include=FALSE}

library(classdata)
data(ames)
head(ames)
?ames

```





The variables for the Ames data are:
Parcel ID: 
Address: 
Style:
Occupancy: 
Sale Date: 
Sale Price: 
Multi Sale:
Year Built:
Acres:
TotalLiving Area:
Bedrooms:
Finished basement:
Lot Area: total area in square feet. It is a dbl object. This variable represents a number for the area of the house yard. The range 
AC: Is a logical variable representing if the house has AC or not. It is a char object, so it will intake Y or N and become True or False.
Fire Place: This is a logical variable representing if a house has a fireplace or not. It is a char object, so it will intake Y or N and become True or False.
Neightborhood: This is a fctr object. It represents the neightborhood area in Ames.





